2nd_draft

### 2020-03-16 src/2nd_draft.Rmd
Update 2nd_draft.Rmd
cv function added

>>>>

```{r}
dummy_year<-dummy(assessment_aggregate$Year)
dummy_municipal<-dummy(assessment_aggregate$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_aggregate$TaxClassCode)
# build x matrix
x<-cbind(dummy_municipal,dummy_year,dummy_taxclass,assessment_aggregate$assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$tax)

y<-assessment_aggregate$rate
x<-cbind(x,y)
# correct col name
#assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$tax
colnames(x)[28:32]<-c("assessTotal","landTotal","improvementTotal","propertyCount","tax")
xm<-x[,1:(ncol(x)-1)]
x.data.frame<-assessment_aggregate
xm.data.frame<-assessment_aggregate[,-8]
y.data.frame<-assessment_aggregate$rate
n <- nrow(xm)
k <- 10
ii <- (1:n)%%k + 1
set.seed(123)
N <- 50
mspe.el<-mspe.la <- mspe.f <- mspe.ri <- mspe.reduced <- rep(0, N)

for (i in 1:N) {
  ii <- sample(ii)
  pr.el<-pr.la <- pr.f <- pr.ri <- pr.reduced <- rep(0, n)
  for (j in 1:k) {
    tmp.ri <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 0, family = "gaussian")
    tmp.la <- cv.glmnet(x = xm[ii != j, ], y = y[ii != j], lambda = lambdas, 
                        nfolds = 10, alpha = 1, family = "gaussian")
    tmp.reduced <- lm(rate ~ factor(Year)+factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc)+assessTotal+landTotal, 
                  data = x.data.frame[ii != j, ])
    tmp.full <- lm(rate ~ factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+tax, 
               data = x.data.frame[ii != j, ])

    tmp.elastic<-train(
      rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+tax, 
      data = x.data.frame[ii != j, ],
      method = "glmnet",
      trControl = cv_10
    )

    pr.ri[ii == j] <- predict(tmp.ri, s = tmp.ri$lambda.min, newx = xm[ii == 
                                                                    j, ])
    pr.la[ii == j] <- predict(tmp.la, s = tmp.la$lambda.min, newx = xm[ii == 
                                                                    j, ])
    pr.reduced[ii == j] <- predict(tmp.reduced, newdata = x.data.frame[ii == j, ])
    pr.f[ii == j] <- predict(tmp.full, newdata = x.data.frame[ii == j, ])

    index<-which.min(tmp.elastic$results$RMSE)
    pr.el[ii == j] <- predict(tmp.elastic, 
                              alpha = tmp.elastic$results[index,1], 
                              lambda = tmp.elastic$results[index,2], 
                              newdata = xm.data.frame[ii == j, ])
  }
  mspe.ri[i]<-mean((y - pr.ri)^2)
  mspe.la[i]<-mean((y - pr.la)^2)
  mspe.reduced[i]<-mean((y - pr.reduced)^2)
  mspe.f[i]<-mean((y - pr.f)^2)
  mspe.el[i]<-mean((y - pr.el)^2)

}
boxplot(mspe.la, mspe.ri,mspe.el, mspe.reduced, mspe.f, 
        names = c("LASSO", "Ridge", "Elastic Net", "Reduced", "Full"), 
        col = c("yellow","steelblue", "gray80", "tomato", "springgreen"), 
        cex.axis = 1, 
        cex.lab = 1, 
        cex.main = 2)
mtext(expression(hat(MSPE)), side = 2, line = 2.5)
